Predator summary

### 2023-02-22 reports/01_predators.qmd
Add effort map

library(targets)
library(tidyverse)

tar_load(c("predators_agg", "ant_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

@@

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = count), data = topfive_stars) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7))
```

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = count), data = soi_stars) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-64, -62, -60, -58)) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  coord_ant(map_lim) +
  theme(axis.text.x = element_text(size = 7))
```

>>>>

library(sf)
library(targets)
library(tidyverse)

tar_load(c("predators_agg", "ant_sf", "effort_sf"), 
         store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

@@

Survey effort. 21 out of the 19404 intervals were recorded as nmi \> 1000 (as opposed to \~1 nmi for the rest). Those intervals excluded from the survey effort.

```{r}
#| label: survey_effort
#| warning: false

effort_stars <- effort_sf %>% 
  filter(nmi < 1000) %>% 
  rasterize_counts(count_col = "nmi",
                   res = 2.5e4)
map_lim <- sf::st_bbox(c(xmin = -65, xmax = -55, ymin = -65, ymax = -58),
                       crs = "EPSG:4326") %>% 
  project_bbox() %>% 
  expand_bbox(factor = 1.2)
ant_basemap(map_lim) + 
  stars::geom_stars(aes(fill = nmi), data = effort_stars) +
  scale_fill_distiller(palette = "PuRd", 
                       direction = 1, 
                       na.value = NA) +
  scale_x_continuous(breaks = seq(-65, -55, by = 5)) +
  scale_y_continuous(breaks = seq(-65, -58, by = 2)) +
  coord_ant(map_lim) +
  facet_wrap(vars(year)) +
  expand_limits(fill = 0)

```

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = log(count + 1)), data = topfive_stars) +
  scale_fill_distiller(palette = "PuRd",
                       direction = 1,
                       na.value = NA) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7))
```

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = log(count + 1)), data = soi_stars) +
  scale_fill_distiller(palette = "PuRd",
                       direction = 1,
                       na.value = NA) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-64, -62, -60, -58)) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  coord_ant(map_lim) +
  theme(axis.text.x = element_text(size = 7))
```
